Towards a classification framework for social machines

### 2013-02-26 latex/paper_new.tex
corrected some missing references
version sent to Nigel and Wendy

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{img/socialmachinescope.png}
\caption{Social machines and related areas} \label{fig:social machine}
\end{center}
\end{figure}

@@

\subsection{Constructs}
The clustering process described in Section~\ref{meth} yielded both a
reduction in the overall number of constructs (in particular an
elimination of over-represented areas) and the identification of three
simple themes: a

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.25\textwidth]{img/socialmachinescope.png}
\caption{Social machines and related areas} \label{fig:socialmachine}
\end{center}
\end{figure}

@@

\subsection{Constructs}
The clustering process described in Section \ref{sec:methodology} yielded both a
reduction in the overall number of constructs (in particular an
elimination of over-represented areas) and the identification of three
simple themes: a
